Efficient Thresholded Correlation using Truncated Singular Value Decomposition

### 2015-08-02 threshold/draft.Rnw
Minor correction.
Fixed the cross-product coefficient.
Fixed the variance.
typo

Even a 1-d projected interval distance threshold may prune many possible
non-adjacent vector pairs with respect to the ordering defined by $P$ as
illustrated by the example in Figure \ref{fig1}.  However, this observation is
unlikely to rule out many adjacent pairs of vectors in most problems.  For
instance, the minimum distance between the points shown in the example in
Figure \ref{fig1} is less than $\sqrt{2(1-t)}/\sigma_1$, and no pruning occurs.

>>>>

Even a 1-d projected interval distance threshold may prune many possible
non-adjacent vector pairs with respect to the ordering defined by $P$ as
illustrated by the example in Figure \ref{fig1}.  However, this observation is
unlikely to rule out many adjacent pairs of vectors in most problems.  For
instance, the maximum distance between adjacent points shown in the example in
Figure \ref{fig1} is less than $\sqrt{2(1-t)}/\sigma_1$, and no pruning occurs.
